Behind Bars: Insights into the Wellbeing of U.S. Prisoners

### 2024-02-16 paper/paper.qmd
discussion finished

>>>>

In conclusion, the findings illuminate an alarming increase in prisoner mortality rates, particularly attributed to cancer and heart
diseases. The persistent rise raises concerns about the overall well-being of incarcerated individuals. The vulnerability
 of inmates to COVID-19, as evidenced by the significantly higher infection rates among prisoners, highlights the
 urgent need for enhanced preventive measures and healthcare within correctional facilities. The study
 uncovers pronounced gender and racial differences in prison mortality. Males exhibit higher mortality
 rates across various causes, emphasizing the need for gender-specific healthcare strategies. Racial differences
 reveal distinct health challenges faced by different groups, necessitating tailored interventions.  Exploring
 the influence of specific prison conditions, such as access to medical care and systemic biases, can provide deeper
 insights. Comparative studies with international datasets may offer a broader perspective on correctional healthcare.
 In all, our paper aims to strengthen the argument that the lack of attention provided to people in correctional
 facilities trying to improve their lives has reached an abysmal state. Instead of paying attention to these concerns
 in society, prisoners are often looked down upon and neglected. Our paper firmly portrays the basic fact that as humans,
even prisoners have rights to access basic healthcare and clean living conditions that will help them in order to grow
into better individuals in the right environment.
